PS753 Glossary

### 2022-01-30 _academics/ps753-glossary/ps753-glossary.Rmd
text updates

---
title: "PS753 Glossary"
description: |
  Glossary page for PS753 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-29
output:
 distill::distill_article:
   self_contained: false
bibliography: PS753.bib
---

@@

# Week 1

**From lecture 1a: [Nodes, Edges and Network Samples](https://www.loom.com/share/efc5252bb75b463481b93e55be6e4d67)**

@@

tie / edge / link
: lines connecting nodes, which indicate some sort of connection or relationship.

node / ego / actor
: $i$ - the node being discussed or focused on

@@

snowball sample
: an entity group formed by starting with "a focal actor or set of actors"^[@hanneman] and "rolling outwards" to its connections until all nodes or actors (in a limited set) are located

@@

**From lecture 1b: [Ties and Adjacency Matrices](https://www.loom.com/share/a64c3a975e7147b9bb06bf921325bd96)**

@@

**From lecture 1c: [Edgelists](https://www.loom.com/share/9232d0ffe78d4ea4affc543bf4e353af)**

@@

---

https://retorque.re/zotero-better-bibtex/

>>>>

---
title: "PS753 Glossary"
description: |
  Glossary for PS753 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-29
output:
 distill::distill_article:
   self_contained: false
   toc: true
bibliography: PS753.bib
---

@@

> **A social network** is a set of actors (or points, or nodes, or agents) that may have relationships (or edges, or ties) with one another. Networks can have few or many actors, and one or more kinds of relations between pairs of actors.
>
>-- <cite>[@hanneman, chapter 2]</cite>

## Week 1

### Class lecture 1a: [Nodes, Edges and Network Samples](https://www.loom.com/share/efc5252bb75b463481b93e55be6e4d67)

@@

tie / edge / link / relation
: lines connecting nodes, which indicate some sort of connection or relationship.

node / ego / actor
: $i$ - the node being discussed or focused on; @hanneman also note "Actors are described by their relations, not by their attributes."

@@

snowball sample
: an entity group formed by starting with "a focal actor or set of actors"^[@hanneman] and "rolling outwards" to its connections until all nodes or actors (in a limited set) are located, or a decision to stop is made

@@

### Class lecture 1b: [Ties and Adjacency Matrices](https://www.loom.com/share/a64c3a975e7147b9bb06bf921325bd96)

@@

### Class lecture 1c: [Edgelists](https://www.loom.com/share/9232d0ffe78d4ea4affc543bf4e353af)

@@

### @hanneman, chapter 1 (Social network data):

binary measures of relations
: undirected relations, 0 or 1 for the absence or presence of a connection

multiple-category nominal measures of relations
: directed relations with categories (like "friend, lover, business relationship, kin, or no relationship")

grouped ordinal measures of relations
: measures that reflect a level of intensity or degree; often turned into binary measures by means of a threshold or cut-off

full-rank ordinal measures of relations
: an ordering from 1 to $n$ of an actor's relations (uncommon in social networks)

interval measures of relations
: continuous measures that express the strength of connections by comparison with others, to be able to say "this tie is twice as strong as that tie"; the "most advanced" level of measurement
